Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-08 paper.tex
small fixes

In this paper, we give a small overview of related work to gather data for flow analysis.
Next, we introduce the iRail query logs, which we study by the means of visualizations.
Finally, we look at public transit data is being published, and how we would be able to get a better indication of travel flows than just mere query logs.

@@

Over the past decade, large datasets have become increasingly commonplace due to the proliferation of sensor networks and portable devices like smartphones.
Termed ``Big Data'' due to the large volume of data records that emerge from real-time sensing\cite{kitchin}, such datasets typically contain information of activities or processes linked to the space and time where they occur.
In the domain of ``Smart City'' research, much has been accomplished with the use of ``Big Data'' to monitor human movement.
Smart card data from public transport systems~\cite{roth,beecham}, taxi journeys~\cite{ferreira} as well as cellular call data~\cite{sevtsuk} have provided planners with new opportunities to develop greater understanding of mobility patterns in urban environments~\cite{batty}.
Yet query logs were, to our knowledge, never used for flow analysis so far.

>>>>

In this paper, we give a small overview of related work to gather data for flow analysis.
Next, we introduce the iRail query logs, which we study by the means of visualizations.
Finally, we look at how public transit data is published and how we would be able to get a better indication of travel flows.

@@

Over the past decade, large datasets have become increasingly commonplace due to the proliferation of sensor networks and portable devices like smartphones.
Termed ``Big Data'' due to the large volume of data records that emerge from real-time sensing~\cite{kitchin}, such datasets typically contain information of activities or processes linked to the space and time where they occur.
In the domain of ``Smart City'' research, much has been accomplished with the use of ``Big Data'' to monitor human movement.
Smart card data from public transport systems~\cite{roth,beecham}, taxi journeys~\cite{ferreira} as well as cellular call data~\cite{sevtsuk} have provided planners with new opportunities to develop greater understanding of mobility patterns in urban environments~\cite{batty}.
Yet query logs were, to our knowledge, never used for flow analysis so far.
